---
title: "{{< fa copyright >}} Curriculum Vitae (Commercial) [{{< fa download >}}](https://www.dropbox.com/s/vhcyj6pz78a51xc/CommercialCv.pdf?dl=0)"
format: html
fontsize: "16px"
toc: true
always_allow_html: true
---


<p style="margin-bottom:-0.2cm;">Luis **Sarmiento**</p>
<p style="margin-bottom:0.15cm;">Environmental Economist</p>

<p style="margin-bottom:-0.15cm;">`r fa("earth-americas")` [luissarmiento.com](luissarmiento.com)</p>

<p style="margin-bottom:-0.15cm;">`r fa("at")` <a href = "mailto: gsaabogado@gmail.com">gsaabogado@gmail.com</a></p>

<p style="margin-bottom:-0.15cm;">`r fa("linkedin")` [luis-sarmiento-eco](https://www.linkedin.com/in/luis-sarmiento-eco)</p>

<p style="margin-bottom:-0.15cm;">`r fa("mobile-button")` +39 030 897890</p>

<p style="margin-bottom:0.5cm;">`r fa("location-dot")` Via Bergognone, 34, 20144 Milan MI, Ital</p>

Applied economist focusing on **causal inference** and **energy modelling**. 


### `r fa("briefcase")` Work  Experience

------------------------------------------------------------------------
```{r}
#| echo: false 
#### Load the excel file ####
file = gsub("/02_cv", "", getwd())
prof = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Occupation")

#### Create the link for the institute ####
prof = mutate(prof, Institution = paste0(link, Institution)) |> 
  select(-link)

#### Construct the table ####
reactable( prof, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  
  columns = list(Dates = colDef(maxWidth = 70),
                 
                 Activities = colDef(maxWidth = 500), 
                 
                 Position = colDef(maxWidth = 100,
                                   style = cell_style(font_color = "#0b263d", font_weight = "bold")), 
                 
                 Institution = colDef(maxWidth = 200, html = TRUE),
                 
                                
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 75, align = "left")))


```

<p style="margin-bottom:1.5cm;">

### `r fa("building-columns")` Education

------------------------------------------------------------------------

```{r}
#| echo: false

#### Load the excel file ####
file = gsub("/02_cv", "", getwd())
educ = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Education")


#### Create the link for the institute ####
educ = mutate(educ, Institution = paste0(link, Institution)) |> 
  select(-link)

#### Create the table ####
reactable(educ, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 500), 
  
  columns = list(Dates = colDef(maxWidth = 100),
                 
                 Dissertation = colDef(maxWidth = 500), 
                 
                 Degree = colDef(maxWidth = 150, align = "center",
                                 style = cell_style(font_color = "#0b263d",
                                                    font_weight = "bold")),
                 
                 Institution = colDef(maxWidth = 150, html = TRUE, align = "center"),
                 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), 
                                  maxWidth = 75, align = "left")))
```

<p style="margin-bottom:1.5cm;">



### `r fa("language")` Softwares and Lenguages

```{r}
#| echo: false 
#| layout-ncol: 2


#### Load the software excel file ####
file = gsub("/02_cv", "", getwd())
soft = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Software")

#### Make the table ####
reactable(
  soft, outlined = F, borderless = T, compact = T, bordered = F, 
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(
    proficiency = colDef(cell = icon_assign(soft, icon = "github", fill_color = "#0b263d"), 
                         name = "", sortable = TRUE), 
    lenguage = colDef(name = ""))
)


#### Load the languages excel file ####
file = gsub("/02_cv", "", getwd())
data = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Languages")

#### Make the table ###
reactable(data, outlined = F, borderless = T, compact = T, bordered = F, 
          
  defaultColDef = colDef(align = "left", maxWidth = 200),
  
  columns = list(proficiency = colDef(cell = icon_assign(data, icon = "earth-americas", fill_color = "#0b263d"), 
                         name = "", sortable = T), 
                 
                 lenguage = colDef(name = "")))


```

<p style="margin-bottom:1.5cm;">

### `r fa("file-zipper")` Publications
```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Publications")

#### Add the link ###
pub = mutate(pub, Article = paste0(link, Article)) |> 
  select(-link)|> 
  select(-Type)

#### Create the table ####
reactable(pub, theme = fivethirtyeight(),
          defaultColDef = colDef(align = "left", maxWidth = 200), 
          
          columns = list(Article = colDef(maxWidth = 500, html = T), 
                         Journal = colDef(maxWidth = 150), 
                         Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                         Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center")))

```


### `r fa("person-chalkboard")` Conference presentations

------------------------------------------------------------------------
```{r}
#| echo: false 

#### Load the data ####
file = gsub("/02_cv", "", getwd())
conf = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Conferences")

#### Construct the table ####
reactable(
  conf, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left"), 
  columns = list(City = colDef(maxWidth = 100), 
                 Conference = colDef(maxWidth = 400),
                 Presentation = colDef(maxWidth = 300),
                 Year = colDef(maxWidth = 50, style = color_scales(conf, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )
```
