---
title: "{{< fa file-contract >}} Applied Econometrics"
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
format: html
fontsize: "0.8em"
toc: true
always_allow_html: true
---
### {{< fa play >}} Introduction

I use state-of-the-art econometric techniques in three main topics:

**The effects of Air Pollution on the Individual**

- What are the effects of air pollution on productivity?
- what are the effects of air pollution on criminality and Domestic Violence?
- What are the effects of air pollution on Decision Making?
- How do the indirect effects of air pollution on children affect the well-being of their parents?

**Air Pollution Control Mechanisms at the City Level**

- How efficient are current policies in reducing the use of internal combustion engines?
- What are the effects of air quality alerts on parents' avoidance behaviour?

**Digitalization, Transport, and Pollution**

- What is the effect of Ride-Hailing Technologies on Urban Air Pollution?

:::{.callout-note}
In the future, I would like to study the effects of climate change on health, labor productivity, and human behavior.
:::

### {{< ai google-scholar >}} Accepted and Published Manuscripts

```{r}
#| echo: false 
pub = data.frame(Year = c(2022, 2021, 2021), 
                 
                 
                 
                 Article = c("The Nonlinear Effects of Pollution on Crime: Evidence from Mexico City and New York",
                             
                              html("<a href='https://onlinelibrary.wiley.com/doi/full/10.1111/sjoe.12458'>Air Pollution 
                                   and the Productivity of High-Skill Labor: Evidence from Court Hearings"), 
                             
                             
                              html("<a href = 'https://www.sciencedirect.com/science/article/abs/pii/S1361920919307278'>The Effects of 
                                   the 2013 Floods on Germany's Road Freight Traffic")), 
                 
                 Journal = c("Environmental Research - Health",
                              "Scandinavian Journal of Economics 124: 301-332.", 
                              "Transportation Research Part D: Transport and the Environment, S.1022774"), 
                 
                 Coauthors = c("",
                                "", 
                                "Julio Fournier"),
                 
                 Institute = c("RFF-CMCC: European Institute on Economics and the Environment", 
                               
                               "RFF-CMCC: European Institute on Economics and the Environment", 
                               
                               "German
                               Institute of Economic Research"),
                 
                 Country = c("https://img.icons8.com/color/344/italy-circular.png", 
                             "https://img.icons8.com/color/344/italy-circular.png",
                             "https://img.icons8.com/color/344/germany-circular.png"))




reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 500, html = TRUE), 
                 Journal = colDef(maxWidth = 250), 
                 Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```

### {{< fa person-praying >}} Working Papers

```{r}
#| echo: false 
pub = data.frame(Start = c(2021, 2019, 2018), 
                 
                 Article = c(html("<a href = 'https://www.rff.org/publications/working-papers/the-air-quality-effects-of-uber/'>
                                  The Air Quality Effects of Uber"),
                             
                              html("<a href =
                              'https://www.rff.org/publications/working-papers/effectiveness-spillovers-and-well-being-effects-of-drivin
                              g-restriction-policies/'>Effectiveness, Spillovers, and Well-Being Effects of Driving Restriction
                              Policies"), 
                              
                             html("<a href = 
                                  'https://www.diw.de/de/diw_01.c.791871.de/publikationen/diskussionspapiere/2020_1877/make_sure_the_kid
                                  s_are_ok__indirect_effects_of_ground-level_ozone_on_well-being.html'>Make Sure the Kids are OK: 
                                  Indirect Effects of Air Pollution on Well-Being")),
                 
                 Status = c("Under Review",
                              "Revise and Resubmit", 
                              "Under Review"),
                 
                 Journal = c("The Review of Economics and Statistics",
                              "Journal of Public Economics", 
                              "Nature Sustainability"), 
                 
                 Coauthors = c("Yeong-Jae Kim",
                                "Nicole Wägner and Aleksandar Zaklan", 
                                "Julia Rechliz, Nicole Wägner, and Aleksandar Zaklan"),
                 
                 Institutes = c("European Institute on Economics and the Environment and KID School of Public Policy", 
                               
                               "European Institute on Economics and the Environment, German
                               Institute of Economic Research, and Leibniz Institute for Economic Research", 
                               
                               "European Institute on Economics and the Environment, German
                               Institute of Economic Research, and Leibniz Institute for Economic Research"))



reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400, html = TRUE), 
                 Journal = colDef(maxWidth = 200), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```

### {{< fa person-digging >}} Underway Research
```{r}
#| echo: false 
pub = data.frame(Start = c(2021,2022, 2020, 2021), 
                 
                 Article = c("The Unaccounted Consequences of Low Emission Zones: Evidence from Madrid Central",
                              "Air Pollution and Court Decisions: Evidence from Ten Million Penal Cases in India", 
                              "Air Quality and School Abenteeism: Evidence from New York City", 
                             "Air Pollution and Domestic Violence"), 
                 
                 Expected = c("Winter 2022",
                              "Spring 2023", 
                              "Spring 2022", 
                              "Spring 2023"),
                 
                 
                 Coauthors = c( "Adrian Santoja and Nicole Wägner",
                                "Adam Nowakowski", 
                                "", 
                                "Ireri Hernandez"),
                 
                 Institutes = c("European Institute on Economics and the Environment, German
                               Institute of Economic Research, and Leibniz Institute for Economic Research",
                               
                               "European Institute on Economics and the Environment and Bocconi University", 
                               
                               "European Institute on Economics and the Environment", 
                               
                               "European Institute on Economics and the Environment and Bocconi University"))



reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400), 
                 Institutes = colDef(maxWidth = 300), 
                 Expected = colDef(maxWidth = 100), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```