---
title: "{{< fa file-contract >}} Applied Econometrics"
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
format: html
fontsize: "0.8em"
toc: true
always_allow_html: true
---

I use state-of-the-art econometric techniques in three main topics:

**The effects of Air Pollution on the Individual**

- What are the effects of air pollution on productivity?
- what are the effects of air pollution on criminality and Domestic Violence?
- What are the effects of air pollution on Decision Making?
- How do the indirect effects of air pollution on children affect the well-being of their parents?

**Air Pollution Control Mechanisms at the City Level**

- How efficient are current policies in reducing the use of internal combustion engines?
- What are the effects of air quality alerts on parents' avoidance behaviour?

**Digitalization, Transport, and Pollution**

- What is the effect of Ride-Hailing Technologies on Urban Air Pollution?

:::{.callout-note}
In the future, I would like to study the effects of climate change on health, labor productivity, and human behavior.
:::

### {{< ai google-scholar >}} Accepted and Published Manuscripts

```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Publications")

#### Add the link and only keep econometrics ###
pub = mutate(pub, Article = paste0(link, Article)) |> 
  select(-link) %>% dplyr::filter(Type == "econometrics") |> 
  select(-Type)


#### Create the table ####
reactable(pub, theme = fivethirtyeight(),
          defaultColDef = colDef(align = "left", maxWidth = 200), 
          
          columns = list(Article = colDef(maxWidth = 500, html = T), 
                         Journal = colDef(maxWidth = 150), 
                         Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                         Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center")))

```

### {{< fa person-praying >}} Working Papers

```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "WorkingPapers")

#### Only keep econometric papers ####
pub = dplyr::filter(pub, Type == "econometrics", WorkingVersion == "Yes") |> 
  select(-Type, -WorkingVersion)


#### Construct table ####
reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left"), 
  columns = list(Article = colDef(maxWidth = 300), 
                 Coauthors = colDef(maxWidth = 150, align = "left"),
                 Journal = colDef(maxWidth = 100, align = "center"), 
                 Status = colDef(maxWidth = 70, align = "center"),
                 Institution = colDef(maxWidth = 300),
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```

### {{< fa person-digging >}} Underway Research
```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "UnderwayResearch")

#### Only keep econometric papers ####
pub = dplyr::filter(pub, Type == "econometrics") |> select(-Type)



reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400), 
                 Institutes = colDef(maxWidth = 300), 
                 Expected = colDef(maxWidth = 100), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```