---
title: "{{< fa solar-panel >}} Energy Modeling"
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
format: html
fontsize: "0.8em"
toc: true
always_allow_html: true
---

### {{< fa play >}} Introduction

I employ techno-economic bottom-up energy models to examine transition pathways of the North-American energy system.

My research answers questions like:

-   What are the effects of variations in natural gas prices on the future of the North American energy system?
-   What is the role of storage technologies in the uptake of renewable energy?
-   What is the future of the Mexican energy system?
-   What are the consequences of changing the dispatch system from merit to physical order dispatch?
-   What are the distributional consequences of high-electrification scenarios in North America?

Besides techno-economic models of the energy system, I am currently developing an Agent-Based Model of technology adoption with my colleagues at the European Institute on Economics and the Environment. The ABM-REN model aims to understand households' decisions to adopt green technologies.

I also contribute to the [37th Energy Modelling Forum](https://emf.stanford.edu/emf-37-deep-decarbonization-high-electrificatio-scenarios-north-america) on high electrification scenarios in North America.

### {{< ai google-scholar >}} Accepted and Published Manuscripts

```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Publications")

#### Add the link and only keep econometrics ###
pub = mutate(pub, Article = paste0(link, Article)) |> 
  select(-link) %>% dplyr::filter(Type == "modeling") |> 
  select(-Type)


#### Create the table ####
reactable(pub, theme = fivethirtyeight(),
          defaultColDef = colDef(align = "left", maxWidth = 200), 
          
          columns = list(Article = colDef(maxWidth = 500, html = T), 
                         Journal = colDef(maxWidth = 150), 
                         Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                         Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center")))

```

### {{< fa person-praying >}} Working Papers

```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "WorkingPapers")

#### Only keep econometric papers ####
pub = dplyr::filter(pub, Type == "modeling", WorkingVersion == "Yes") |> 
  select(-Type, -WorkingVersion) 


#### Construct table ####
reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left"), 
  columns = list(Article = colDef(maxWidth = 300), 
                 Coauthors = colDef(maxWidth = 150, align = "left"),
                 Journal = colDef(maxWidth = 100, align = "center"), 
                 Status = colDef(maxWidth = 70, align = "center"),
                 Institution = colDef(maxWidth = 300),
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )



```

### {{< fa person-digging >}} Underway Research

```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "UnderwayResearch")

#### Only keep econometric papers ####
pub = dplyr::filter(pub, Type == "modeling") |> select(-Type)


#### Present the table ####
reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400), 
                 Institutes = colDef(maxWidth = 300), 
                 Expected = colDef(maxWidth = 100), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```
