---
title: ""
format:
  pdf:
    css: custom.scss
    include-in-header: 
       text: |
         \usepackage{multicol}
         \usepackage{xcolor}
         \definecolor{light}{HTML}{42647c}
         \definecolor{highlight}{HTML}{800080}
         \definecolor{dark}{HTML}{330033}
         \usepackage{hyperref}
         \hypersetup{colorlinks=true, urlcolor = light}
    urlcolor:  light
    geometry:
      - top=20mm
      - left=20mm
      - left=20mm
---


\normalsize Dr. Luis <span style="color:red;">Sarmiento</span> \vspace{-0.2cm}

\footnotesize Environmental Economist

\scriptsize 

`r fa("earth-americas")` **[luissarmiento.com](https://luissarmiento.com)** \vspace{-0.2cm}

`r fa("linkedin")` **[luis-sarmiento-eco](https://www.linkedin.com/in/luis-sarmiento-eco)** \vspace{-0.2cm}

`r fa("at")` **[gsaabogado\@gmail.com](gsaabogado\@gmail.com)** \vspace{-0.2cm}


\vspace{0.25cm}

\hrulefill

\scriptsize As an experienced professional, I have developed a strong expertise in applied econometrics, energy modeling, and agent-based models. My research focuses on critical issues such as the sub-clinical effects of air pollution (productivity, well-being), city policies to decrease environmental externalities, the energy transition, and climate change.

\vspace{-0.1cm}

\hrulefill

### `r fa("briefcase")` <span style="color:red;">Work Experience</span> \vspace{-0.4 cm}

```{r}
#| echo: false 
#| warning: false

#### Load the excel file ####
file = gsub("/02_cv", "", getwd())
prof = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Occupation")

#### Exclude the link ####
prof = select(prof, -link )

#### Create the table ####
table = reactable( prof, theme = fivethirtyeight(font_size = 13),
  defaultColDef = colDef(align = "center", maxWidth = 200, vAlign = "center",
                         cell = data_bars(fill_color = "red")), 
  
  columns = list(Dates = colDef(maxWidth = 70),
                 
                 Activities = colDef(maxWidth = 400, html = TRUE, align = "left"), 
                 
                 Position = colDef(maxWidth = 150,vAlign = "center"), 
                 
                 Institution = colDef(maxWidth = 200, html = TRUE, align = "center"),
                 
                                
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 75, align = "left")))


#### Take an screen shot of the html output ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 30, 930, 370), delay = 0.5)


```

### `r fa("building-columns")` Education \vspace{-0.4 cm}

```{r}
#| echo: false
#| fig-width: 10
#| fig-height: 4
#| warning: false


#### Load the excel file ####
file = gsub("/02_cv", "", getwd())
educ = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Education")

#### Take away variables that I do not use ####
educ = select(educ, -link)

#### Construct the table ####
table = reactable(educ, theme = fivethirtyeight(font_size = 13),
  defaultColDef = colDef(align = "center", maxWidth = 400, vAlign = "center"), 
  
  columns = list(Dates = colDef(maxWidth = 70),
                 
                 Dissertation = colDef(maxWidth = 400), 
                 
                 Degree = colDef(maxWidth = 150, align = "center"),
                 
                 Institution = colDef(maxWidth = 200, html = TRUE, align = "center"),
                 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), 
                                  maxWidth = 75, align = "left")))

#### Save the table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 190), zoom = 2)


```

### `r fa("person-chalkboard")` Teaching \vspace{-0.4 cm}

```{r}
#| echo: false
#| fig-width: 10
#| fig-height: 4
#| warning: false

#### Load the data ####
file = gsub("/02_cv", "", getwd())
conf = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Teaching")

#### Construct the table ####
table = reactable(
  conf, theme = fivethirtyeight(font_size = 13),
  defaultColDef = colDef(align = "center"), 
  columns = list(Level = colDef(maxWidth = 100), 
                 Institute = colDef(maxWidth = 600),
                 Semester = colDef(maxWidth = 100),
                 Lecture = colDef(maxWidth = 600),
                 Year = colDef(maxWidth = 50, style = color_scales(conf, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

#### Save the table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 220))
```

### `r fa("file-zipper")` Publications \vspace{-0.4cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Publications")

#### Exclude not-necessary columns ####
pub = select(pub, -link, -Type, -Country)

#### Construct the table ####
table = reactable(pub, theme = fivethirtyeight(font_size = 13),
          defaultColDef = colDef(align = "left", maxWidth = 200, html = T, vAlign = "center"), 
          
          columns = list(Article = colDef(maxWidth = 500, html = T), 
                         Journal = colDef(maxWidth = 150), 
                         Authors = colDef(maxWidth = 150),
                         Affiliations = colDef(maxWidth = 250),
                         Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                         Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center")))

#### Take the screen shot ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 480))

```


### `r fa("person-chalkboard")` Latest Presentations \vspace{-0.4cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4

#### Load the data ####
file = gsub("/02_cv", "", getwd())
conf = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Conferences")


### Only keep the last eight conferences ####
conf = conf[1:5,]


table = reactable(conf, theme = flatly(font_size = 13),
                  
  defaultColDef = colDef(align = "left", maxWidth = 200),
  
  columns = list(City = colDef(maxWidth = 100), 
                 Conference = colDef(maxWidth = 350), 
                 Presentation = colDef(maxWidth = 350),
                 Year = colDef(maxWidth = 50, 
                               style = color_scales(conf,  colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center")))
  
#### Screen-shot the languages table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 270), zoom = 2)


```

### `r fa("language")` Softwares and Lenguages \vspace{-0.4cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4
#| layout-ncol: 2

#### Load the software excel file ####
file = gsub("/02_cv", "", getwd())
soft = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Software")

#### Create the Software Table ####
table = reactable(theme = flatly(font_size = 13),
                  soft, outlined = F, borderless = T, compact = T, bordered = F, 
                  defaultColDef = colDef(align = "left", maxWidth = 200), 
                  columns = list(
                    proficiency = colDef(cell = icon_assign(soft, icon = "github", fill_color = "#0b263d"), 
                                         name = "", sortable = TRUE), 
                    
                    lenguage = colDef(name = "")))

#### Screen-shot the software table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(20, 35, 370, 200))


#### Load the languages excel file ####
file = gsub("/02_cv", "", getwd())
data = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Languages")

#### Create the Languages Table ####
table = reactable(theme = flatly(font_size = 13),
                  data, outlined = F, borderless = T, compact = T, bordered = F, 
                  defaultColDef = colDef(align = "left", maxWidth = 200), 
                  columns = list(
                    proficiency = colDef(cell = icon_assign(data, icon = "earth-americas", fill_color = "#0b263d"), 
                                         name = "", sortable = TRUE), lenguage = colDef(name = ""))
)

#### Screen-shot the languages table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(20, 35, 370, 200))

```