---
title: "{{< fa book-open-reader >}} Curriculum Vitae"
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
format: html
fontsize: "0.8em"
toc: true
always_allow_html: true
---

<p style="margin-bottom:-0.2cm;">Luis **Sarmiento**</p>
<p style="margin-bottom:0.15cm;">Environmental Economist</p>

<p style="margin-bottom:-0.15cm;">{{< fa earth-americas >}} luis.sarmiento.net</p>

<p style="margin-bottom:-0.15cm;">{{< fa at >}} gsaabogado\@gmail.com</p>

<p style="margin-bottom:-0.15cm;">{{< fa brands linkedin >}} [luis-sarmiento-eco](https://www.linkedin.com/in/luis-sarmiento-eco)</p>

<p style="margin-bottom:-0.15cm;">{{< fa mobile-button >}} +39 030 897890</p>

<p style="margin-bottom:0.5cm;">{{< fa location-dot >}} Via Bergognone, 34, 20144 Milan MI, Ital</p>

Applied economist focusing on **causal inference**. Current research activities encompass : looking at the effects of **air pollution** on human well-being, studying the intersection between **digitalization** and **environmental degradation**, and analyzing pathways for the **decarbonization** of the energy sector.

### {{< fa briefcase >}} Professional Experience

------------------------------------------------------------------------
```{r}
#| echo: false 
position = c("Junior Scientist", "Postdoc Researcher", 
             "Research Associate", "Research Associate", 
             "Business Executive")

startdates = c("Sep.2022 -", "Sep.2020 Sep.2022", 
               "Apr.2017 Sep.2020", "Nov.2019 Aug.2020", 
               "Sep.2012 Sep.2015")

institution = c(html("<a href='https://www.eiee.org/'>RFF-CMCC: European Institute on Economics and the 
                     Environment</a>"), 
                html("<a href='https://www.eiee.org/'>RFF-CMCC: European Institute on Economics and the 
                     Environment</a>"), 
                html("<a
                     href='https://www.diw.de/en'>DIW-Berlin: German Institute of Economic Research</a>"),
                html("<a href='https://www.hertie-school.org/en/'>Hertie School of Governance</a>"), 
                
                html("<a href='https://www.bb.com.mx/webcenter/portal/BanBajio/home?_afrRedirect=64903577593997558'>Ban
                     co del Bajio SA </a>"))


activities = c("Scientific support to institutional projects, Mentoring of junior Scholars, applied econometrics, and 
               the development of agent-based models, Study the relationship between the transportation sector, 
               digitalization, and the environment as part of the EU 2D4D project.", 
               
               "Study the relationship between the transportation sector, digitalization, and the environment; Applied 
               econometric projects on air pollution, air pollution control policies, and natural disasters, Scientific
               support to institutional projects.", 
               
               "Research and publication of scientific articles in the realm of energy and environmental economics; 
               Research projects on the effects of air pollution and air pollution control policies on productivity, 
               health, and wellbeing.", 
               
               "Study the relationship between daylight savings and transit patterns.", 
               
               "Financial advice to small and midium-sized companies")

countries = c("https://img.icons8.com/color/344/italy-circular.png",
              "https://img.icons8.com/color/344/italy-circular.png",
              "https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/mexico-circular.png")

prof = data.frame(Dates = startdates, Position = position, 
                  Institution = institution, Country = countries,  `Activities` = activities)


reactable(
  prof, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Dates = colDef(maxWidth = 70),
                 
                 Activities = colDef(maxWidth = 500), 
                 
                 Position = colDef(maxWidth = 100,
                                   style = cell_style(font_color = "#0b263d", font_weight = "bold")), 
                 
                 Institution = colDef(maxWidth = 200, 
                                      html = TRUE),
                 
                                
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 75, align = "left")), 
  
  )


```

<p style="margin-bottom:1.5cm;">

### {{< fa building-columns >}} Education

------------------------------------------------------------------------

```{r}
#| echo: false
degree = c("Doctor in Economics (Summa Cum Laude)", 
           "Master of Science in Economics and Management", 
           "Bachelor of International Business")

dates = c("2017-2020", "2014-2016", "2007-2012")


institution = c(html("<a href='https://www.tu.berlin/en/'>Berlin Institute of Technology</a>"),
                html("<a href='https://www.hu-berlin.de/en'>Humboldt University of Berlin</a>"),
                 html("<a href='https://bajio.delasalle.edu.mx/'>University of Lasalle Bajio</a>"))


dissertation = c("An Econometric Analysis of Envvironmental Phenomena", 
                 "Electricity Production from Renewable Sources in Mexico: A Time Series Analysis", 
                 "A Project of Foreign Direct Investment between Mexico and Colombia") 

countries = c("https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/mexico-circular.png")
          

educ = data.frame(Dates = dates, Degree = degree,
                  Institution = institution, 
                  Country = countries, Dissertation = dissertation)




reactable(
  educ, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Dates = colDef(maxWidth = 100),
                 Dissertation = colDef(maxWidth = 400), 
                 Degree = colDef(maxWidth = 150, 
                                  style = cell_style(font_color = "#0b263d", font_weight = "bold")), 
                 Institution = colDef(maxWidth = 200, html = TRUE),
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 75, align = "left"))
  )
```

<p style="margin-bottom:1.5cm;">

### {{< fa book-open >}} Research Interests


```{r}
#| echo: false 
topics <- c("Applied Econometrics", "Digitalization and the Environment", "Energy Modeling", "Agent Based Models")
details2 <- c("Use of econometric methods for causal inference", 
              "Analysis of the inter-dependenencies between the transportation sector, digitalization, and the environment", 
              
              "Design and Implementation of optimization models to assess public policies for the decabornization of energy systems",
              
              "Design and implementation of agent-based models to understand households' adoption of green technologies ")


awards <- data.frame(topics,details2)


kable(align = 'rl',awards, booktabs= T,col.names = NULL) %>%
  kable_styling(font_size = 12.5) %>%
  column_spec(1, bold = T, color = "#696969", width = "12em") %>%
  column_spec(2, bold = FALSE, color = "#696969", width = "52.5em") %>%
  kable_styling(bootstrap_options ="hover")
```

<p style="margin-bottom:0.5cm;">

### {{< fa language >}} Softwares and Lenguages

```{r}
#| echo: false 
#| layout-ncol: 2
soft <- data.frame(lenguage = c("R (R-Studio)", "Quarto", "Markdown", "Git", "GAMS", "Julia", "Python" ), proficiency = c(5,5,5,5,3,2,2))


   

reactable(
  soft, outlined = F, borderless = T, compact = T, bordered = F, 
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(
    proficiency = colDef(cell = icon_assign(soft, icon = "github", fill_color = "#0b263d"), 
                         name = "", sortable = TRUE), lenguage = colDef(name = ""))
)


data <- data.frame(lenguage = c("English", "Spanish", "Italian", "German"), proficiency = c(5,5,4,3))
data$proficiency <- as.numeric(as.character(data$proficiency))

reactable(
  data, outlined = F, borderless = T, compact = T, bordered = F, 
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(
    proficiency = colDef(cell = icon_assign(data, icon = "earth-americas", fill_color = "#0b263d"), 
                         name = "", sortable = TRUE), lenguage = colDef(name = ""))
)


```

<p style="margin-bottom:1.5cm;">

### {{< ai archive >}} Publications
```{r}
#| echo: false 
pub = data.frame(Year = c(2022, 2021, 2021, 2021, 2021, 2019), 
                 
                 
                 
                 Article = c( html("<a href='https://doi.org/10.1088/2752-5309/ac9a65'>The Nonlinear 
                                   Effects of Pollution on Crime: Evidence from Mexico City and New York"),
                             
                              html("<a href='https://onlinelibrary.wiley.com/doi/full/10.1111/sjoe.12458'>Air Pollution 
                                   and the Productivity of High-Skill Labor: Evidence from Court Hearings"), 
                             
                              html("<a href='https://www.sciencedirect.com/science/article/abs/pii/S0301421521002482'>Mexico and US 
                              Power Systems Under Variations in Natural Gas Prices</a>"), 
                                   
                              html("<a href='https://www.sciencedirect.com/science/article/abs/pii/S0301421521000288'>The Role of Energy
                              Storage in the Uptake of Renewable Energy: A Model Comparison Approach"),
                             
                              html("<a href = 'https://www.sciencedirect.com/science/article/abs/pii/S1361920919307278'>The Effects of 
                                   the 2013 Floods on Germany's Road Freight Traffic"), 
                             
                              html("<a href= 'https://www.mdpi.com/1996-1073/12/17/3270'>Analysing Scenarios for the Integration of 
                                   Renewable Energy Sources in the Mexican Energy System")), 
                 
                 Journal = c("Environmental Research - Health",
                              "Scandinavian Journal of Economics 124: 301-332.", 
                              "Energy Policy, 151, 113378", 
                              "Energy Policy 151, 112159", 
                              "Transportation Research Part D: Transport and the Environment, S.1022774", 
                              "Energies, 12.17, 3270"), 
                 
                 Coauthors = c("",
                                "", 
                                "Juan Rosellon, Sauleh Sidiqui, Max Brown, Avraam Charalampos, Anahi Molar, Baltazar Solano", 
                                "Sara Giarola, Kathleen Vaillancourt, Max Brown, Anahi Molar, Ivan Garcia Kerdan", 
                                "Julio Fournier", 
                                "Thorstan Burandt, Konstantin Löffler, Pao-yu Oei"),
                 
                 Institute = c("RFF-CMCC: European Institute on Economics and the Environment", 
                               
                               "RFF-CMCC: European Institute on Economics and the Environment and German
                               Institute of Economic Research", 
                               
                               "RFF-CMCC: European Institute on Economics and the Environment and German
                               Institute of Economic Research", 
                               
                               "RFF-CMCC: European Institute on Economics and the Environment and German
                               Institute of Economic Research", 
                               
                               "German Institute of Economic Research", 
                               
                               "German Institute of Economic Research"),
                 
                 Country = c("https://img.icons8.com/color/344/italy-circular.png", 
                             "https://img.icons8.com/color/344/italy-circular.png",
                             "https://img.icons8.com/color/344/italy-circular.png", 
                             "https://img.icons8.com/color/344/italy-circular.png", 
                             "https://img.icons8.com/color/344/germany-circular.png", 
                             "https://img.icons8.com/color/344/germany-circular.png"))




reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 500, html = TRUE), 
                 Journal = colDef(maxWidth = 150), 
                 Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```

### {{< fa person-digging >}} Working Papers
```{r}
#| echo: false 
pub = data.frame(Start = c(2021, 2019, 2018, 2021,2022, 2020), 
                 
                 Article = c("The Air Quality Effects of Uber", 
                              "Effectiveness, Spillovers, and Well-Being Effects of Driving Restriction Policies", 
                              "Make Sure the Kids are OK: Indirect Effects of Air Pollution on Well-Being",
                             "The Unaccounted Consequences of Low Emission Zones: Evidence from Madrid Central",
                              "Air Pollution and Court Decisions: Evidence from Ten Million Penal Cases in India", 
                              "The Agent Base Model of Technology Adoption ABM-REN"), 
                 
                 Status = c("Under Review",
                              "Revise and Resubmit", 
                              "Under Review", 
                            "Working Paper",
                              "Working Paper", 
                              "Working Paper"),
                 
                 Journal = c("The Review of Economics and Statistics",
                              "Journal of Public Economics", 
                              "Nature Sustainability", 
                              "", 
                              "", 
                             ""), 
                 
                 Coauthors = c("Yeong-Jae Kim",
                                "Nicole Wägner and Aleksandar Zaklan", 
                                "Julia Rechliz, Nicole Wägner, and Aleksandar Zaklan", 
                               "Adrian Santoja and Nicole Wägner",
                                "Adam Nowakowski", 
                                "Severin Reissl and Johanness Emmerling"),
                 
                 Institutes = c("European Institute on Economics and the Environment and KID School of Public Policy", 
                               
                               "European Institute on Economics and the Environment, German
                               Institute of Economic Research, and Leibniz Institute for Economic Research", 
                               
                               "European Institute on Economics and the Environment, German
                               Institute of Economic Research, and Leibniz Institute for Economic Research", 
                               
                               "European Institute on Economics and the Environment, German
                               Institute of Economic Research, and Leibniz Institute for Economic Research",
                               
                               "European Institute on Economics and the Environment and Bocconi University", 
                               
                               "European Institute on Economics and the Environment"))



reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400), 
                 Journal = colDef(maxWidth = 200), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```
### {{< fa person-chalkboard >}} Latest Conference and Presentations

------------------------------------------------------------------------
```{r}
#| echo: false 
conference <- c("EAERE Annual Conference", 
                "Mannheim Energy and Environmental Conference",
                "BSE Workshop: The Distributional Consequences of Environmental Policies", 
                "CMCC Annual Conference", 
                "EAERE Annual Conference", 
                "Verein für Socialpolitik", 
                "EAERE Annual Conferece", 
                "Seventh Latin-American Meeting of Energy Economics", 
                "World Congress of Environmental and Resource Economists", 
                "Meeting of the Latin-American and Caribbean Economic Association", 
                "Essen Health Conference", 
                "Mannheim Energy Conference", 
                "European Conference of the International Association of Energy Economists")


presentation <- c("The Air Quality Effects of Uber", 
                "The Unaccounted Effects of Low Emission Zones: Evidence from Madrid Central",
                "The Air Quality Effects of Uber", 
                "Towards the Debornization of the Transportation Sector", 
                "The Nonlinear Effects of Pollution on Crime: Evidence from Mexico City and New York", 
                "Make Sure the Kids are OK: Indirect Effects of Air Pollution on Well-Being", 
                "Air Pollution and the Productivity of High-Skill Labor: Evidence from Court Hearings", 
                "Analysing Scenarios for the Integration of Renewable Energy Sources in the Mexican Energy System", 
                "External costs of electricity transmission infrastructure: evidence from well-being data", 
                "Air Pollution and the Productivity of High-Skill Labor: Evidence from Court Hearings", 
                "Make Sure the Kids are OK: Indirect Effects of Air Pollution on Well-Being", 
                "External costs of electricity transmission infrastructure: evidence from well-being data", 
                "External costs of electricity transmission infrastructure: evidence from well-being data")


place = c("Rimini", 
          "Mannheim",
          "Berlin",
          "Lecce", 
          "Berlin", 
          "Leipzig", 
          "Manchester", 
          "Buenos Aires", 
          "Götheborg", 
          "Guayaquil", 
          "Essen", 
          "Mannheim", 
          "Vienna")

year = c("2022", "2022", "2022", "2021", "2020", "2019", 
         "2019", "2019", "2018", "2018", "2017", "2017", "2017")


country = c("https://img.icons8.com/color/344/italy-circular.png", 
            "https://img.icons8.com/color/344/germany-circular.png",
            "https://img.icons8.com/color/344/germany-circular.png", 
            "https://img.icons8.com/color/344/italy-circular.png", 
            "https://img.icons8.com/color/344/germany-circular.png", 
            "https://img.icons8.com/color/344/germany-circular.png", 
            "https://img.icons8.com/fluency/344/england-circular.png",
            "https://img.icons8.com/fluency/344/argentina-circular.png",
            "https://img.icons8.com/color/344/sweden-circular.png",
            "https://img.icons8.com/color/344/ecuador-circular.png",
            "https://img.icons8.com/color/344/germany-circular.png",
            "https://img.icons8.com/color/344/germany-circular.png",
            "https://img.icons8.com/color/344/austria-circular.png")

conf <- data.frame(conference, presentation,city = place,country, year) |> mutate(year = as.numeric(year))


reactable(
  conf, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(city = colDef(maxWidth = 100), 
                 conference = colDef(maxWidth = 350), 
                 presentation = colDef(maxWidth = 350),
                 year = colDef(maxWidth = 50, style = color_scales(conf, colors = c("gray", "#0b263d"))), 
                 country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )
```
