---
title: "{{< fa solar-panel >}} Energy Modeling"
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
format: html
fontsize: "0.8em"
toc: true
always_allow_html: true
---

### {{< fa play >}} Introduction

I employ techno-economic bottom-up energy models to examine transition pathways of the North-American energy system.

My research answers questions like:

-   What are the effects of variations in natural gas prices on the future of the North American energy system?
-   What is the role of storage technologies in the uptake of renewable energy?
-   What is the future of the Mexican energy system?
-   What are the consequences of changing the dispatch system from merit to physical order dispatch?
-   What are the distributional consequences of high-electrification scenarios in North America?

Besides techno-economic models of the energy system, I am currently developing an Agent-Based Model of technology adoption with my colleagues at the European Institute on Economics and the Environment. The ABM-REN model aims to understand households' decisions to adopt green technologies.

I also contribute to the [37th Energy Modelling Forum](https://emf.stanford.edu/emf-37-deep-decarbonization-high-electrificatio-scenarios-north-america) on high electrification scenarios in North America.

### {{< ai google-scholar >}} Accepted and Published Manuscripts

```{r}
#| echo: false 
pub = data.frame(Year = c(2021, 2021, 2019), 
                 
                 
                 
                 Article = c( html("<a href='https://www.sciencedirect.com/science/article/abs/pii/S0301421521002482'>Mexico and US 
                              Power Systems Under Variations in Natural Gas Prices</a>"), 
                                   
                              html("<a href='https://www.sciencedirect.com/science/article/abs/pii/S0301421521000288'>The Role of 
                              Energy Storage in the Uptake of Renewable Energy: A Model Comparison Approach"),
                          
                             
                              html("<a href= 'https://www.mdpi.com/1996-1073/12/17/3270'>Analysing Scenarios for the Integration of 
                                   Renewable Energy Sources in the Mexican Energy System")), 
                 
                 Journal = c("Energy Policy, 151, 113378", 
                              "Energy Policy 151, 112159", 
                              "Energies, 12.17, 3270"), 
                 
                 Coauthors = c("Juan Rosellon, Sauleh Sidiqui, Max Brown, Avraam Charalampos, Anahi Molar, Baltazar Solano", 
                                "Sara Giarola, Kathleen Vaillancourt, Max Brown, Anahi Molar, Ivan Garcia Kerdan", 
                                "Thorstan Burandt, Konstantin Löffler, Pao-yu Oei"),
                 
                 Institute = c("RFF-CMCC: European Institute on Economics and the Environment and German
                               Institute of Economic Research", 
                               
                               "RFF-CMCC: European Institute on Economics and the Environment and German
                               Institute of Economic Research", 
                               
                               "RFF-CMCC: European Institute on Economics and the Environment and German
                               Institute of Economic Research"),
                 
                 Country = c("https://img.icons8.com/color/344/italy-circular.png", 
                             "https://img.icons8.com/color/344/italy-circular.png",
                             "https://img.icons8.com/color/344/germany-circular.png"))




reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 500, html = TRUE), 
                 Journal = colDef(maxWidth = 150), 
                 Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```

### {{< fa person-praying >}} Working Papers

```{r}
#| echo: false 
pub = data.frame(Start = c(2021), 
                 
                 Article = c(html("<a href = 'https://www.rff.org/publications/working-papers/effect-of-changing-marginal-cost-to-physical-order-dispatch-in-the-power-sector/'>
                                  The Effect of Changing Marginal Cost to Physical Order Dispatch in the Power Sector")),
                 
                 Status = c("Working Paper"),
                 
                 Journal = c(""), 
                 
                 Coauthors = c("Juan Rosellon and Raul Gutierrez"),
                 
                 Institutes = c("European Institute on Economics and the Environment University of Chicago, and CIDE Mexico"))



reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400, html = TRUE), 
                 Journal = colDef(maxWidth = 200), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```

### {{< fa person-digging >}} Underway Research

```{r}
#| echo: false 
pub = data.frame(Start = c(2021,2022), 
                 
                 Article = c("The Mexico-US Interconnection Under High Electrification Scenarios", 
                             "Distributional and Equity Outcomes under EMF-37"), 
                 
                 Expected = c("summer 2023",
                              "Autum 2023"),
                 
                 
                 Coauthors = c( "Raul Gutierrez and Juan Rosellon",
                                "John Bistline, Morgan Browning, Jim McFarland, Chikara Onda, Noah Sandoval, John Weyant"),
                 
                 Institutes = c("European Institute on Economics and the Environment, University of Chicago, and CIDE Mexico", 
                                "European Institute on Economics and the Environment, EPRI, EPA, DOW, NREL, Standford University"))



reactable(
  pub, theme = fivethirtyeight(),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400), 
                 Institutes = colDef(maxWidth = 300), 
                 Expected = colDef(maxWidth = 100), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

```
