---
title: ""
format:
  pdf:
    theme: flatly
    documentclass: scrartcl
    colorlinks: true
    linkcolor: "EF58A0"
    geometry:
      - top=10mm
      - left=15mm
      - left=15mm
    fontsize: "10pt"
---

Luis **Sarmiento** \vspace{-0.15cm}

Environmental Economist

\vspace{-0.25cm}
\noindent \rule{5cm}{1pt}
\vspace{0.25cm}


`r fa("earth-americas")` luissarmiento.com \vspace{-0.2cm}

`r fa("at")` gsaabogado\@gmail.com \vspace{-0.2cm}

`r fa("linkedin")` [luis-sarmiento-eco](https://www.linkedin.com/in/luis-sarmiento-eco) \vspace{-0.15cm}

`r fa("mobile-button")` +39 030 897890 \vspace{-0.15cm}

`r fa("location-dot")` Via Bergognone, 34, 20144 Milan MI, Italy \vspace{-0.15cm}

\vspace{0.5 cm}

Applied economist focusing on **causal inference** and **energy modelling**.

## `r fa("briefcase")` Work Experience \vspace{-0.5cm}

\hrulefill

\vspace{-0.15cm}

```{r}
#| echo: false 
#| warning: false
position = c("Junior Scientist", "Postdoc Researcher", 
             "Research Associate", "Research Associate", 
             "Business Executive")

startdates = c("Sep.2022 -", "Sep.2020 Sep.2022", 
               "Apr.2017 Sep.2020", "Nov.2019 Aug.2020", 
               "Sep.2012 Sep.2015")

institution = c(html("RFF-CMCC: European Institute on Economics and the 
                     Environment"), 
                html("RFF-CMCC: European Institute on Economics and the 
                     Environment"), 
                html("DIW-Berlin: German Institute of Economic Research"),
                html("Hertie School of Governance"), 
                html("Banco del Bajio SA"))


activities = c("Scientific support to institutional projects, Mentoring of junior Scholars, applied econometrics, and 
               the development of agent-based models, Study the relationship between the transportation sector, 
               digitalization, and the environment as part of the EU 2D4D project.", 
               
               "Study the relationship between the transportation sector, digitalization, and the environment; Applied 
               econometric projects on air pollution, air pollution control policies, and natural disasters, Scientific
               support to institutional projects.", 
               
               "Research and publication of scientific articles in the realm of energy and environmental economics; 
               Research projects on the effects of air pollution and air pollution control policies on productivity, 
               health, and wellbeing.", 
               
               "Study the relationship between daylight savings and transit patterns.", 
               
               "Financial advice to small and midium-sized companies")

countries = c("https://img.icons8.com/color/344/italy-circular.png",
              "https://img.icons8.com/color/344/italy-circular.png",
              "https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/mexico-circular.png")

prof = data.frame(Dates = startdates, Position = position, 
                  Institution = institution, Country = countries,  `Activities` = activities)


table = reactable(
  prof, theme = flatly(),
  defaultColDef = colDef(align = "left", maxWidth = 500), 
  columns = list(Dates = colDef(maxWidth = 70),
                 
                 Activities = colDef(maxWidth = 500), 
                 
                 Position = colDef(maxWidth = 150,
                                   style = cell_style(font_color = "#0b263d", font_weight = "bold")), 
                 
                 Institution = colDef(maxWidth = 200, 
                                      html = TRUE),
                 
                                
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 75, align = "left")), 
  
  )

 
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 30, 930, 360))


```

## `r fa("building-columns")` Education \vspace{-0.5cm}

\hrulefill

\vspace{-0.15cm}

```{r}
#| echo: false
#| fig-width: 10
#| fig-height: 4
degree = c("Doctor in Economics (Summa Cum Laude)", 
           "Master of Science in Economics and Management", 
           "Bachelor of International Business")

dates = c("2017-2020", "2014-2016", "2007-2012")


institution = c(html("Berlin Institute of Technology"),
                html("Humboldt University of Berlin"),
                 html("University of Lasalle Bajio"))


dissertation = c("An Econometric Analysis of Envvironmental Phenomena", 
                 "Electricity Production from Renewable Sources in Mexico: A Time Series Analysis", 
                 "A Project of Foreign Direct Investment between Mexico and Colombia") 

countries = c("https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/germany-circular.png",
              "https://img.icons8.com/color/344/mexico-circular.png")
          

educ = data.frame(Dates = dates, Degree = degree,
                  Institution = institution, 
                  Country = countries, Dissertation = dissertation)




table = reactable(
  educ, theme = flatly(),
  defaultColDef = colDef(align = "center", maxWidth = 500), 
  
  columns = list(Dates = colDef(maxWidth = 100),
                 Dissertation = colDef(maxWidth = 500), 
                 Degree = colDef(maxWidth = 150, style = cell_style(font_color = "#0b263d", font_weight = "bold")), 
                 Institution = colDef(maxWidth = 200, html = TRUE),
                 Country = colDef(cell = embed_img(height = "25", width = "25"), 
                                  maxWidth = 75, align = "left"))
  )


html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 220), zoom = 2)


```

### `r fa("book-open")` Research Interests


```{r}
#| echo: false 
topics <- c("Applied Econometrics", "Digitalization and the Environment", "Energy Modeling", "Agent Based Models")
details2 <- c("Use of econometric methods for causal inference", 
              "Analysis of the inter-dependenencies between the transportation sector, digitalization, and the environment", 
              
              "Design and Implementation of optimization models to assess public policies for the decabornization of energy systems",
              
              "Design and implementation of agent-based models to understand households' adoption of green technologies ")


awards <- data.frame(topics,details2)


kable(align = 'rl',awards, booktabs= T,col.names = NULL, format = "latex") %>%
  kable_styling(font_size = 10.5) %>%
  column_spec(1, bold = T, width = "12em") %>%
  column_spec(2, bold = FALSE, width = "52.5em") %>%
  kable_styling(latex_options = c("HOLD_position", "scale_down", "striped"))
```

## `r fa("language")` Softwares and Lenguages

```{r}
#| echo: false 
#| layout-ncol: 2
soft <- data.frame(
  lenguage = c("R (R-Studio)", "Quarto", "Markdown", "Git", "GAMS", "Julia", "Python" ), 
  proficiency = c(5,5,5,5,3,2,2), 
  idiom = c("English", "Spanish", "Italian", "German", "", "", ""), 
  proficiency2 = c(5,5,4,3, 0,0, 0))


   

table = reactable(
  soft, outlined = F, borderless = T, compact = T, bordered = F, 
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(
    proficiency = colDef(cell = icon_assign(soft, icon = "github", fill_color = "#0b263d"), 
                         name = "", sortable = TRUE), 
    
    proficiency2 = colDef(cell = icon_assign(soft, icon = "github", fill_color = "#0b263d"), 
                         name = "", sortable = TRUE),
    
    lenguage = colDef(name = ""), idiom = colDef(name = ""))
)


html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(20, 35, 930, 220), zoom = 2)

```






