---
title: ""
format:
  pdf:
    include-in-header: 
       text: |
         \usepackage{multicol}
    theme: flatly
    documentclass: scrartcl
    colorlinks: false
    linkcolor: "EF58A0"
    geometry:
      - top=10mm
      - left=15mm
      - left=15mm
---


\LARGE Dr. Luis **Sarmiento** \vspace{-0.15cm}

\small Environmental Economist

\scriptsize 

`r fa("earth-americas")` [luissarmiento.com](https://www.linkedin.com/in/luis-sarmiento-eco) \vspace{-0.2cm}

`r fa("at")` gsaabogado\@gmail.com \vspace{-0.2cm}

`r fa("linkedin")` [luis-sarmiento-eco](https://www.linkedin.com/in/luis-sarmiento-eco) \vspace{-0.2cm}

`r fa("mobile-button")` +39 030 897890 \vspace{-0.2cm}

`r fa("location-dot")` Via Bergognone, 34  20144, Milan MI, Italy 

\vspace{0.25cm}

\footnotesize Applied economist focusing on causal inference. Current research activities encompass: looking at the effects of air pollution on
human well-being, studying the intersection between digitalization and environmental degradation, and analyzing pathways for
the decarbonization of the energy sector.


### `r fa("briefcase")` Work Experience \vspace{-0.5cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4

#### Load the excel file ####
file = gsub("/02_cv", "", getwd())
prof = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Occupation")

#### Exclude the link ####
prof = select(prof, -link )

#### Create the table ####
table = reactable(prof, theme = flatly(font_size = 16),
                  
                  defaultColDef = colDef(align = "left"), 
                  
                  columns = list(Dates = colDef(maxWidth = 100),
                                 
                                 Activities = colDef(maxWidth = 700), 
                                 
                                 Position = colDef(maxWidth = 100, align = "center",
                                                   style = cell_style(font_color = "#0b263d", font_weight = "bold")), 
                                 
                                 Institution = colDef(maxWidth = 200, html = TRUE, align = "center"),
                                 
                                 Country = colDef(cell = embed_img(height = "25", width = "25"), 
                                                  maxWidth = 75, align = "left")))

#### Take an screen shot of the html output ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 30, 930, 420), zoom = 2)


```

### `r fa("building-columns")` Education \vspace{-0.4 cm}

```{r}
#| echo: false
#| fig-width: 10
#| fig-height: 4
#| warning: false


#### Load the excel file ####
file = gsub("/02_cv", "", getwd())
educ = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Education")

#### Take away variables that I do not use ####
educ = select(educ, -link)

#### Construct the table ####
table = reactable(
  educ, theme = flatly(font_size = 16),
  defaultColDef = colDef(align = "left", maxWidth = 500), 
  
  columns = list(Dates = colDef(maxWidth = 100),
                 
                 Dissertation = colDef(maxWidth = 300), 
                 
                 Degree = colDef(maxWidth = 200, align = "center",
                                 style = cell_style(font_color = "#0b263d",
                                                    font_weight = "bold")),
                 
                 Institution = colDef(maxWidth = 200, html = TRUE, align = "center"),
                 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), 
                                  maxWidth = 75, align = "left"))
)


html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 220), zoom = 2)


```

### `r fa("book-open")` Research Interests \vspace{-0.4cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4
#### Load the excel file ####
file = gsub("/02_cv", "", getwd())
int = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Research Interests")

#### Create the table ####
table = reactable(int, theme = nytimes(font_size = 16),
                  
                  defaultColDef = colDef(align = "left", maxWidth = 500), 
                  
                  columns = list(topics = colDef(maxWidth = 300, header = "", 
                                                 align = "right", 
                                                 style = cell_style(font_color = "#0b263d", font_weight = "bold")),
                                 
                                 details = colDef(maxWidth = 700, header = "")))

#### Take an screen shot of the html output ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 30, 930, 200), zoom = 2)

```


### `r fa("language")` Softwares and Lenguages \vspace{-0.4cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4
#| layout-ncol: 2

#### Load the software excel file ####
file = gsub("/02_cv", "", getwd())
soft = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Software")

#### Create the Software Table ####
table = reactable(theme = flatly(font_size = 15),
                  soft, outlined = F, borderless = T, compact = T, bordered = F, 
                  defaultColDef = colDef(align = "left", maxWidth = 200), 
                  columns = list(
                    proficiency = colDef(cell = icon_assign(soft, icon = "github", fill_color = "#0b263d"), 
                                         name = "", sortable = TRUE), 
                    
                    lenguage = colDef(name = "")))

#### Screen-shot the software table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(20, 35, 370, 170), zoom = 2)


#### Load the languages excel file ####
file = gsub("/02_cv", "", getwd())
data = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Languages")

#### Create the Languages Table ####
table = reactable(theme = flatly(font_size = 15),
                  data, outlined = F, borderless = T, compact = T, bordered = F, 
                  defaultColDef = colDef(align = "left", maxWidth = 200), 
                  columns = list(
                    proficiency = colDef(cell = icon_assign(data, icon = "earth-americas", fill_color = "#0b263d"), 
                                         name = "", sortable = TRUE), lenguage = colDef(name = ""))
)

#### Screen-shot the languages table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(20, 35, 370, 150), zoom = 2)

```


### `r fa("file-zipper")` Publications \vspace{-0.4cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Publications")

#### Exclude not-necessary columns ####
pub = select(pub, -link, -Type, -Institute, -Country)

#### Construct the table ####
table = reactable(
  pub, theme = flatly(font_size = 16),
  defaultColDef = colDef(align = "left", maxWidth = 500), 
  columns = list(Article = colDef(maxWidth = 600, html = TRUE), 
                 Journal = colDef(maxWidth = 200), 
                 Coauthors = colDef(maxWidth = 300),
                 Year = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))))
)

#### Take the screen shot ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 350), zoom = 2)

```

### `r fa("person-praying")` Working Papers \vspace{-0.4cm}
```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "WorkingPapers")

#### Exclude not-necessary columns ####
pub = pub |>  dplyr::filter(WorkingVersion == "Yes") |> 
  select(-Type, -WorkingVersion, -Institute)

#### Construct the table ####
table = reactable(
  pub, theme = flatly(font_size = 16),
  defaultColDef = colDef(align = "left", maxWidth = 500), 
  
  columns = list(Article = colDef(maxWidth = 600), 
                 Status = colDef(maxWidth = 150),
                 Journal = colDef(maxWidth = 200),
                 Coauthors = colDef(maxWidth = 300),
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
)

#### Make the screen-shot ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 260), zoom = 2)

```
### `r fa("person-digging")` Underway Research \vspace{-0.4cm}
```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "UnderwayResearch")

#### Only keep relevant studies ####
pub = select(pub, -Type)[1:2,]

#### Construct the table ####
table = reactable(
  pub, theme = flatly(font_size = 16),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400), 
                 Institutes = colDef(maxWidth = 300), 
                 Expected = colDef(maxWidth = 100), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

#### Make the screen-shot ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 200), zoom = 2)

```


### `r fa("person-digging")` Underway Research (Cont.) \vspace{-0.4cm}
```{r}
#| echo: false 
#### Load the data ####
file = gsub("/02_cv", "", getwd())
pub = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "UnderwayResearch")

#### Only keep relevant studies ####
pub = select(pub, -Type)[2:8,]

#### Construct the table ####
table = reactable(
  pub, theme = flatly(font_size = 16),
  defaultColDef = colDef(align = "left", maxWidth = 200), 
  columns = list(Article = colDef(maxWidth = 400), 
                 Institutes = colDef(maxWidth = 300), 
                 Expected = colDef(maxWidth = 100), 
                 Start = colDef(maxWidth = 50, style = color_scales(pub, colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center"))
  )

#### Make the screen-shot ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 500), zoom = 2)

```

### `r fa("person-chalkboard")` Latest Presentations \vspace{-0.4cm}

```{r}
#| echo: false 
#| warning: false
#| fig-width: 10
#| fig-height: 4

#### Load the data ####
file = gsub("/02_cv", "", getwd())
conf = read_excel(paste0(file, "/Codebook.xlsx"), sheet = "Conferences")


### Only keep the last eight conferences ####
conf = conf[1:8,]


table = reactable(conf, theme = flatly(font_size = 16),
                  
  defaultColDef = colDef(align = "left", maxWidth = 200),
  
  columns = list(City = colDef(maxWidth = 100), 
                 Conference = colDef(maxWidth = 350), 
                 Presentation = colDef(maxWidth = 350),
                 Year = colDef(maxWidth = 50, 
                               style = color_scales(conf,  colors = c("gray", "#0b263d"))), 
                 Country = colDef(cell = embed_img(height = "25", width = "25"), maxWidth = 100, align = "center")))
  
#### Screen-shot the languages table ####
html = "table.html"
htmlwidgets::saveWidget(table, html)
webshot2::webshot(html, "table.png", cliprect = c(40, 35, 930, 470), zoom = 2)


```
